ms_figures

### 2018-10-05 man/ms_figures.Rmd
change plot orientation S5
update

```{r, warning=FALSE, out.extra='angle=90', fig.height=5}
# see trends-resilience_bai.Rmd 
df <- read.csv(file=here::here('/out/bai_resiliences_severes' ,'resiliences_bai_droughts.csv'), header=TRUE)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="black") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=4, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    xlab(XLab) + ylab(YLab) + 
    geom_text_repel() + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE) +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 14, 
                                    face = "bold.italic",
                                    margin = margin(b = -15)), 
          axis.title.y = element_blank())
  }

@@

sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resistance (Rt) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5, titulo = "Rt")

sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Recovery (Rc) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5, titulo = "Rc")

sevRt + sevRc + sevRs

>>>>

```{r, warning=FALSE, dpi = 100, fig.height=5}
# ```{r, warning=FALSE, out.extra='angle=90', fig.height=4, fig.width=2}
# see trends-resilience_bai.Rmd 
df <- read.csv(file=here::here('/out/bai_resiliences_severes' ,'resiliences_bai_droughts.csv'), header=TRUE)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="black") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=2, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    xlab(XLab) + ylab(YLab) + 
    geom_text_repel() + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE) +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 8, 
                                    face = "bold.italic",
                                    margin = margin(b = -15)), 
          axis.title.y = element_blank())
  }

@@

sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "", YLab = "Resistance (Rt) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5, titulo = "Rt")

sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "", YLab = "Recovery (Rc) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5, titulo = "Rc")

sevRt + sevRc + sevRs + plot_layout(nrow = 1)
